---
title: "DDP Course Project: Shiny Application and Reproducible Pitch"
author: "BNL"
date: "19 jul 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This presentation was built as part of an assignment for the course **Developing Data Products** as part of the Coursera **Data Science Specialization**.

The app developed as a part of this assignment is avalilable at: <https://blundbye.shinyapps.io/Course_project_week4/>.

The source code for the app (the ui.R and server.R files) are available on the GitHub repo: <https://github.com/blundbye/DDP_CourseProject/>.

## Web Application Functionality

- This app generates the linear fit of *Price* vs. *Carat mass* from a sample set of data points from the *diamonds* data set.
- In order to get the fitted values (the red line) the user has to brush over at least 5 observations.
- The app then calculates and shows the slope and intercept of the fitted line in the side panel.
- The user can also select the level(s) of quality of the diamonds

## The Data Input

A description of the diamonds data set can be found [Here](http://ggplot2.tidyverse.org/reference/diamonds.html).

```{r, message=FALSE, warning=FALSE}
# load data
library(plotly)
data("diamonds")
```

As can be seen below the data set consist of 53.940 rows and 10 variables:

```{r, echo=TRUE, message=FALSE, warning=FALSE}
dim(diamonds)
```

Since that probably wil be too much data for our app to perform well, we'll use a sample of just 100 observations (and we only care of diamonds with af carat greater than 0.5):

```{r, echo=TRUE, message=FALSE, warning=FALSE}
set.seed(2017-07-17)
d <- diamonds[diamonds$carat > .5,][sample(nrow(diamonds[diamonds$carat > .5,]), 100), ]
head(d)
```


## Snapshot of the app

```{r, echo=FALSE}
library(png)
library(grid)
snap <- readPNG("C:/Privat/Uddannelse/Coursera/Data_Products/Course_project_week4/snapshot.png")
 grid.raster(snap)
```


